Analyzing Network Transfer Protocols on a Simulated Interplanetary Internet

### 2024-04-10 paper/paper.tex
add abstract

\begin{abstract}
    TODO insert abstract here
\end{abstract}

>>>>

\begin{abstract}
  This paper discusses interplanetary networks, the challenges that can arise
  from them that make them a unique challenge compared to shorter-range computer
  networks, and the protocols that can be used in this type of network. In
  addition, we look at how one can use conventional network simulators to test
  interplanetary network implementations. We used the network simulator
  NS-3~\cite{ns-3} to test various transport layer protocols against each other
  in a network topology that we designed in the network simulator to emulate
  long-distance communications. Using this network simulation, we were able to
  compare UDP, TCP, and TCP New Reno protocols against each other to see how
  they each performed across such large distances with high delays.
\end{abstract}
